---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# elm

<!-- badges: start -->
<!-- badges: end -->

The goal of elm is to provide a file size exploration tool that allows you to visualize 
  multiple files on your computer in an interactive way using R. With Elm, you can 
  view your files in a variety of different ways, including a treemap (by size and file 
  type), other charts, or a directory tree. Elm makes it easy to gain insights into the files on your computer, helping you to manage your storage more effectively.

## Installation

You can install the development version of elm like so:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/elm")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(elm)
library(dplyr)
```

You can visualize your folders or files using `elm_treemap_*()` functions:
```{r, eval = FALSE}
elm_treemap_dir()
elm_treemap_file()
```

Here's an example of how you can copy your folder or file directory to your clipboard:
```{r}
elm_clip_dir()
```

```{r}
elm_clip_files()
```






